Open Data Quality is Poor but Slowly Improving

### 2021-01-27 outputs/paper/paper.Rmd
fix table widths

The Toronto Open Data Portal was launched in 2009, following the increasing public interest in accessible and free data [@aboutportal]. The push for open data is a global trend, often linked to the ideas of open government, democratic participation, and civic empowerment [@Sayago]. Ten years after the portal’s launch, technical abilities and expectations for open data had risen significantly [@aboutportal], leading the Open Data Toronto team to consider how the success of the portal could best be measured [@HernandezMedium1]. Beginning in December 2019, A Data Quality Score system was developed. In keeping with the spirit of open data, complete scoring results are available on the portal.

@@

  # Style the table:
  kableExtra::kable_styling(latex_options = "scale_down")
```

@@

  # Manipulate colors, labels, and scales for easier presentation:
  scale_color_gradientn(colors = c('darkturquoise', 'royalblue2', 'magenta3')) +
  labs(color = "Average Quality score \n across all packages",
    x = "Date recorded",
    y = "Number of packages scored",
    title = "Scoring Frequency Increased Over the Beta Testing Period")+ 
  scale_x_datetime( breaks = date_breaks("2 months"),
                    minor_breaks = date_breaks("1 month"),
                    labels = date_format("%b%d'%y",tz="EST"), # Format the x-axis scale to show Mar13'21, for example
                    expand = c(0,0), # spaces out scale labels for legibility
                    limits = as.POSIXct(strptime(c("2019-12-02 00:00", "2021-01-25 00:00"), # set x-axis limits
                    format = "%Y-%m-%d %H:%M"))) +
  theme_light()
```

>>>>

The Toronto Open Data Portal was launched in 2009, following the increasing public interest in accessible and free data [@aboutportal]. The push for open data is a global trend, often linked to the ideas of open government, democratic participation, and civic empowerment [@Sayogo]. Ten years after the portal’s launch, technical abilities and expectations for open data had risen significantly [@aboutportal], leading the Open Data Toronto team to consider how the success of the portal could best be measured [@HernandezMedium1]. Beginning in December 2019, A Data Quality Score system was developed. In keeping with the spirit of open data, complete scoring results are available on the portal.

@@

  # Style the table:
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "6em") %>%
  column_spec(6, width = "7em") %>%
  column_spec(7, width = "5em") %>%
  column_spec(8, width = "5em") %>%
  column_spec(9, width = "5em") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

@@

  # Manipulate colors, labels, and scales for easier presentation:
  scale_color_gradientn(colors = c('darkturquoise', 'royalblue2', 'magenta3')) +
  labs(color = "Average \nQuality \nscore \nacross all \npackages",
    x = "Date recorded",
    y = "Number of packages scored",
    title = "Scoring Frequency Increased Over the Beta Testing Period")+ 
  scale_x_datetime( breaks = date_breaks("2 months"),
                    minor_breaks = date_breaks("1 month"),
                    labels = date_format("%b%d'%y",tz="EST"), # Format the x-axis scale to show Mar13'21, for example
                    expand = c(0,0), # spaces out scale labels for legibility
                    limits = as.POSIXct(strptime(c("2019-12-02 00:00", "2021-01-25 00:00"), # set x-axis limits
                    format = "%Y-%m-%d %H:%M"))) +
  theme_light()
```
